\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2016-04-21 mSystems/mSys_MAIN.tex
MINOR: rename mySys_ file prefix to mSys_ prefix
On branch master
	renamed:    mySys_MAIN.pdf -> mSys_MAIN.pdf
	renamed:    mySys_MAIN.tex -> mSys_MAIN.tex
	renamed:    mySys_MandM.tex -> mSys_MandM.tex
	renamed:    mySys_discussion.tex -> mSys_discussion.tex
	renamed:    mySys_intro.tex -> mSys_intro.tex
	renamed:    mySys_results.tex -> mSys_results.tex
	renamed:    mySys_suppl_0.1.tex -> mSys_suppl_0.1.tex
For mSystems paper, include new watermark with the release number
On branch master
	modified:   mSys_MAIN.pdf
	modified:   mSys_MAIN.tex
Move text from mSys_MandM.tex to intro, and other

@@

@@

% watermark (time consuming!)
\newwatermark[allpages,color=red!4,angle=45,scale=9,xpos=-40,ypos=0]{DRAFT}

@@

%===================================== SECTIONS =======================================
%%% Introduction
\section*{Introduction}
\input{mySys_intro.tex}   
%%% Result
\section*{Results}
\input{mySys_results.tex}
%%% Discussion
\section*{Discussion}
\input{mySys_discussion.tex}    
%%% Material & Methods
\section*{Materials and Methods}
\input{mySys_MandM.tex}

@@

\newpage
\begin{thebibliography}{99}
\bibitem{moving} Caporaso, J.G. et al. Moving pictures of the human microbiome. {\it Genome Biol.} {\bf 12,} R50 (2011).
\bibitem{LEA} Faith, J.J. et al. The long-term stability of the human gut microbiota. {\it Science} {\bf 341,} 1237439 (2013).
\bibitem{kwashiorkor} Smith M.I. et al. Gut microbiomes of Malawian twin pairs discordant for kwashiorkor. {\it Science} {\bf 339,} 548-54 (2013).
\bibitem{diet} David, L.A. et al. Diet rapidly and reproducibly alters the human gut microbiome. {\it Nature} {\bf 505,} 559-63 (2014).
\bibitem{antibiotic} Dethlefsen L., Relman D. A. Incomplete recovery and individualized responses of the human distal gut microbiota to repeated antibiotic perturbation. {\it Proc. Nat. Acad. Sci. USA} {\bf 108,} 4554-61 (2011).
\bibitem{IBS} Durban, A. \textit{et al.} Structural alterations of faecal and mucosa-associated bacterial communities in irritable bowel syndrome. {\it FEMS Microbiol. Ecol.} {\bf 86}, 581-9 (2013).
\bibitem{QIIME} Caporaso, J.G. et al. QIIME allows analysis of high-throughput community sequencing data. {\it Nature Methods} {\bf 7,} 335-6 (2010).
\bibitem{LMAT} Ames, S.K. et al. Scalable metagenomic taxonomy classification usng a reference genome database. {\it Bioinformatics} {\bf 29,} 2253-2260 (2013).
\bibitem{fs} Eisler,Z., Bartos,I., Kertesz,J. Fluctuation scaling in complex systems: Taylor's law and beyond. {\it Adv. Phys.} {\bf 57,} 85 (2008).
\bibitem{taylor} Taylor, L.R. Aggregation, Variance and the mean. {\it Nature} {\bf 189,} 732-35 (1961).
\bibitem{stat} Jorgensen,B., Martinez,J.R., Tsao,M. Asymptotic behaviour of the variance function. {\it Scand. J. Statist..} {\bf 21,} 223-243 (1994).
\bibitem{convergence1} Fronczak,A., Fronczak,P. Origins of Taylor's power law for fluctuation scaling in complex systems. {\it Phys. Rev. E} {\bf 81,} 066112 (2010).
\bibitem{convergence2} Kendal, W.S., Jorgensen,B. Taylor's power law and fluctuation scaling explained by a central-limit-like convergence. {\it Phys. Rev. E} {\bf 83,} 066115 (2011).
\bibitem{convergence3} Kendal, W.S., Jorgensen,B. Tweedie convergence: A mathematical basis for Taylor's power law. {\it Phys. Rev. E} {\bf 84,} 066120 (2011).
\bibitem{ranking} Blumm, N. et al. Dynamics of ranking processes in complex systems. {\it Phys. Rev. Lett.} {\bf 109,} 128701 (2012).
	\bibitem{FD} Weber, J. \textit{et al.} Fluctuation dissipation theorem. {\it Phys. Rev.} {\bf 101}, 1620-6 (1956).
	\bibitem{FASTX} Gordon, A., Hannon, G.J. FASTX-Toolkit. FASTQ/A shortreads pre-processing tools (2010). http://hannonlab.cshl.edu/fastx\_toolkit/ (accessed 23 Feb 2015).
	\bibitem{SILVA} Quast C.  \textit{et al.} The SILVA ribosomal RNA gene database project: improved data processing and web-based tools (2013)
 	\bibitem{ecology} Xiao Xiao, Ethan P. White, Mevin B. Hooten, and Susan L. Durham. On the use of log-transformation vs. nonlinear regression for analyzing biological power laws. {\it Ecology} {\bf 92}, 10, 1887-1894 (2011).
 	\bibitem{genR2} Magee L., $R^2$ measures based on wald and likelihood ratio joint significance tests. {\it The American Statistician} {\bf 44}, 3, 250-253 (1990).
	\bibitem{disR2} Nagelkerke N.J.D., A note on a general definition of the coefficient of determination. {\it Biometrika} {\bf 78}, 3, 691-692 (1991).
	\bibitem{boot} Wu, C.F.J. Jackknife, bootstrap and other resampling methods in regression analysis. (with discussions) \textit{The Annals of Statistics} {\bf 14}: 1261?1350 (1986)
\end{thebibliography}
\todo{Eliminar \textit{et al.} y poner la referencia completa como exige la guía de estilo de la revista...}

>>>>

% release codenumber (update it here!)
\newcommand\releasecode{0.0.3}

@@

% watermarks (time consuming!)
%\newwatermark[allpages,color=red!4,angle=45,scale=9,xpos=-40,ypos=0]{DRAFT}
%\newwatermark[allpages,color=red!12,angle=0,scale=1,xpos=0,ypos=137]{
%\emph{mSystems} \LaTeX\ manuscript release \releasecode}

@@

@@

%===================================== SECTIONS =======================================
%%% Introduction
\section*{Introduction}
\input{mSys_intro.tex}   
%%% Result
\section*{Results}
\input{mSys_results.tex}
%%% Discussion
\section*{Discussion}
\input{mSys_discussion.tex}    
%%% Material & Methods
\section*{Materials and Methods}
\input{mSys_MandM.tex}

@@

\newpage
\begin{thebibliography}{99}
\bibitem{diabetes2} {\bf Qin J, Li Y, Cai Z, Li S, Zhu J, Zhang F, Liang S, Zhang W, Guan Y, Shen D, Peng Y, Zhang D, Jie Z, Wu W, Qin Y, Xue W, Li J, Han L, Lu D, Wu P, Dai Y, Sun X, Li Z, Tang A, Zhong S, Li X, Chen W, Xu R, Wang M, Feng Q, Gong M, Yu J, Zhang Y, Zhang M, Hansen T, Sanchez G, Raes J, Falony G, Okuda S, Almeida M, LeChatelier E, Renault P, Pons N, Batto J-M, Zhang Z, Chen H, Yang R, Zheng W, Li S, Yang H, Wang J, Ehrlich SD, Nielsen R, Pedersen O, Kristiansen K, Wang J.} 2012. A metagenome-wide association study of gut microbiota in type 2 diabetes. Nature {\bf 490}:55–60.
\bibitem{CVD} {\bf Brown JM, Hazen SL.} 2015. The Gut Microbial Endocrine Organ: Bacterially Derived Signals Driving Cardiometabolic Diseases. Annu Rev Med {\bf 66}:343–359.
\bibitem{IBS} {\bf Durbán A, Abellán JJ, Jiménez-Hernández N, Artacho A, Garrigues V, Ortiz V, Ponce J, Latorre A, Moya A.} 2013. Instability of the faecal microbiota in diarrhoea-predominant irritable bowel syndrome. FEMS Microbiol Ecol {\bf 86}:581–589.
\bibitem{CD} {\bf Gevers D, Kugathasan S, Denson LA, Vázquez-Baeza Y, Van Treuren W, Ren B, Schwager E, Knights D, Song SJ, Yassour M, Morgan XC, Kostic AD, Luo C, González A, McDonald D, Haberman Y, Walters T, Baker S, Rosh J, Stephens M, Heyman M, Markowitz J, Baldassano R, Griffiths A, Sylvester F, Mack D, Kim S, Crandall W, Hyams J, Huttenhower C, Knight R, Xavier RJ.} 2014. The treatment-naive microbiome in new-onset Crohn’s disease. Cell Host Microbe {\bf 15}:382–392.
\bibitem{ob1} {\bf Ridaura VK, Faith JJ, Rey FE, Cheng J, Duncan AE, Kau L, Griffi NW, Lombard V, Henrissat B, Bain JR, Michael J, Ilkayeva O, Semenkovich CF, Funai K, Hayashi DK, Lyle J, Martini MC, Ursell LK, Clemente JC, Treuren W Van, William A, Knight R, Newgard CB, Heath AC, Gordon JI, Kau AL, Griffin NW, Muehlbauer MJ.} 2013. Gut Microbiota from Twins Discordant for Obesity Modulate Metabolism in Mice Gut Microbiota from Twins Metabolism in Mice. Science {\bf 341}:1241214.
\bibitem{ob2} {\bf Turnbaugh PJ, Hamady M, Yatsunenko T, Cantarel BL, Duncan A, Ley RE, Sogin ML, Jones WJ, Roe BA, Affourtit JP, Egholm M, Henrissat B, Heath AC, Knight R, Gordon JI.} 2009. LETTERS A core gut microbiome in obese and lean twins. Nature {\bf 457}:480–484.
\bibitem{nutr} {\bf Subramanian S, Huq S, Yatsunenko T, Haque R, Mahfuz M, Alam MA, Benezra A, DeStefano J, Meier MF, Muegge BD, Barratt MJ, VanArendonk LG, Zhang Q, Province MA, Petri WA, Ahmed T, Gordon JI.} 2014. Persistent gut microbiota immaturity in malnourished Bangladeshi children. Nature {\bf 510}:417–21.
\bibitem{moving} Caporaso, J.G. et al. Moving pictures of the human microbiome. {\it Genome Biol.} {\bf 12,} R50 (2011).
\bibitem{LEA} Faith, J.J. et al. The long-term stability of the human gut microbiota. {\it Science} {\bf 341,} 1237439 (2013).
\bibitem{kwashiorkor} Smith M.I. et al. Gut microbiomes of Malawian twin pairs discordant for kwashiorkor. {\it Science} {\bf 339,} 548-54 (2013).
\bibitem{diet} David, L.A. et al. Diet rapidly and reproducibly alters the human gut microbiome. {\it Nature} {\bf 505,} 559-63 (2014).
\bibitem{antibiotic} Dethlefsen L., Relman D. A. Incomplete recovery and individualized responses of the human distal gut microbiota to repeated antibiotic perturbation. {\it Proc. Nat. Acad. Sci. USA} {\bf 108,} 4554-61 (2011).
\bibitem{QIIME} Caporaso, J.G. et al. QIIME allows analysis of high-throughput community sequencing data. {\it Nature Methods} {\bf 7,} 335-6 (2010).
\bibitem{LMAT} Ames, S.K. et al. Scalable metagenomic taxonomy classification usng a reference genome database. {\it Bioinformatics} {\bf 29,} 2253-2260 (2013).
\bibitem{fs} Eisler,Z., Bartos,I., Kertesz,J. Fluctuation scaling in complex systems: Taylor's law and beyond. {\it Adv. Phys.} {\bf 57,} 85 (2008).
\bibitem{taylor} Taylor, L.R. Aggregation, Variance and the mean. {\it Nature} {\bf 189,} 732-35 (1961).
\bibitem{stat} Jorgensen,B., Martinez,J.R., Tsao,M. Asymptotic behaviour of the variance function. {\it Scand. J. Statist..} {\bf 21,} 223-243 (1994).
\bibitem{convergence1} Fronczak,A., Fronczak,P. Origins of Taylor's power law for fluctuation scaling in complex systems. {\it Phys. Rev. E} {\bf 81,} 066112 (2010).
\bibitem{convergence2} Kendal, W.S., Jorgensen,B. Taylor's power law and fluctuation scaling explained by a central-limit-like convergence. {\it Phys. Rev. E} {\bf 83,} 066115 (2011).
\bibitem{convergence3} Kendal, W.S., Jorgensen,B. Tweedie convergence: A mathematical basis for Taylor's power law. {\it Phys. Rev. E} {\bf 84,} 066120 (2011).
\bibitem{ranking} Blumm, N. et al. Dynamics of ranking processes in complex systems. {\it Phys. Rev. Lett.} {\bf 109,} 128701 (2012).
	\bibitem{FD} Weber, J. \textit{et al.} Fluctuation dissipation theorem. {\it Phys. Rev.} {\bf 101}, 1620-6 (1956).
	\bibitem{FASTX} Gordon, A., Hannon, G.J. FASTX-Toolkit. FASTQ/A shortreads pre-processing tools (2010). http://hannonlab.cshl.edu/fastx\_toolkit/ (accessed 23 Feb 2015).
	\bibitem{SILVA} Quast C.  \textit{et al.} The SILVA ribosomal RNA gene database project: improved data processing and web-based tools (2013)
 	\bibitem{ecology} Xiao Xiao, Ethan P. White, Mevin B. Hooten, and Susan L. Durham. On the use of log-transformation vs. nonlinear regression for analyzing biological power laws. {\it Ecology} {\bf 92}, 10, 1887-1894 (2011).
 	\bibitem{genR2} Magee L., $R^2$ measures based on wald and likelihood ratio joint significance tests. {\it The American Statistician} {\bf 44}, 3, 250-253 (1990).
	\bibitem{disR2} Nagelkerke N.J.D., A note on a general definition of the coefficient of determination. {\it Biometrika} {\bf 78}, 3, 691-692 (1991).
	\bibitem{boot} Wu, C.F.J. Jackknife, bootstrap and other resampling methods in regression analysis. (with discussions) \textit{The Annals of Statistics} {\bf 14}: 1261?1350 (1986)
\end{thebibliography}
\todo{Eliminar \textit{et al.} y poner la referencia completa como exige la guía de estilo de la revista...}

### 2016-04-21 mSystems/mSys_intro.tex
intro added to MAIN; new refs added to intro

The desire to understand the factors that influence human health and cause diseases has always been one of the major driving forces of biological research. We are populated by a myriad of microorganisms that are interacting with us in several physiological processes such as metabolism regulation or maturation of the immune system. Human microbiota has been suggested to be closely related to diseases like type 2 diabetes [ref], cardiovascular disease (CVD) [ref], irritable bowel syndrome [ref], Crohn?s disease [ref] or some affections as obesity [ref] or malnutrition [ref]. High throughput methods for microbial 16S ribosomal RNA gene and WGS have now begun to reveal the composition of archaeal, bacterial, fungal and viral communities located both, in and on the human body. Modern high-throughput sequencing and bioinformatics tools provide a powerful means of understanding how the human microbiome contributes to health and its potential as a target for therapeutic interventions [ref?].

>>>>

The desire to understand the factors that influence human health and cause diseases has always been one of the major driving forces of biological research. We are populated by a myriad of microorganisms that are interacting with us in several physiological processes such as metabolism regulation or maturation of the immune system. Human microbiota has been suggested to be closely related to diseases like type 2 diabetes 
\cite{diabetes2}, cardiovascular disease (CVD) \cite{CVD}, irritable bowel syndrome \cite{IBS}, Crohn's disease \cite{CD} or some affections as obesity \cite{ob1, ob2} or malnutrition \cite{nutr}. High throughput methods for microbial 16S ribosomal RNA gene and WGS have now begun to reveal the composition of archaeal, bacterial, fungal and viral communities located both, in and on the human body. Modern high-throughput sequencing and bioinformatics tools provide a powerful means of understanding how the human microbiome contributes to health and its potential as a target for therapeutic interventions [ref?].
